An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-01-01 EconGrowth2.Rnw
Added a note about comparing ternary plots from CD and CES models.
Changed country order. Fixes Issue #23.

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

@@

Figure~\ref{fig:CES_ternary_graph} shows 
$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
      labs(x=expression(a[0]), y=expression(c[t])) +
       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

>>>>

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevs, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

@@

Figure~\ref{fig:CES_ternary_graph} shows 
$\alpha$, $\beta$, and $\gamma$ parameters for the CES model for all nests and countries.
Figure~\ref{fig:CES_ternary_graph} is comparable to
the ternary graph for the Cobb-Douglas models, 
Figure~\ref{fig:CD_Ternary_Scatter_Graph}.

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevs)
  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
      labs(x=expression(a[0]), y=expression(c[t])) +
       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@
